Co-citations in context

### 2019-06-10 cocit_r.tex
fixed citep

\citep{uzzi_atypical_2013} used a novel approach for co-citation analysis using, as input, 17.9 million articles and their cited references, from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research. In this study, co-citation frequencies of references in were calculated and represented as journal pairs (observed co-citation frequencies). Expected values of these frequencies were generated from Monte Carlo simulations under a random graph model. Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed \emph{z-scores}, which were interpreted as suggesting conventional thought if positive and novel thought if negative. Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its refernces. For each article, positional statistics of z-scores were calculated to set thresholds for a binary (high/low) classification of conventionality (C) using the median and novelty (N) using the tenth percentile of z-scores within an article. Thus, HCLN would denote high conventionality and low novelty with all four combinations being possible. 
\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a 'nearly universal` recipe for impact.

>>>>

\cite{uzzi_atypical_2013} used a novel approach for co-citation analysis using, as input, 17.9 million articles and their cited references, from the Web of Science (WoS)  to characterize a subset of highly cited articles with respect to both novel and conventional combinations of prior research. In this study, co-citation frequencies of references in were calculated and represented as journal pairs (observed co-citation frequencies). Expected values of these frequencies were generated from Monte Carlo simulations under a random graph model. Observed frequencies were then normalized (shifted and scaled) to averaged expected values from ten simulations and termed \emph{z-scores}, which were interpreted as suggesting conventional thought if positive and novel thought if negative. Consequently, every article was associated with multiple z-scores corresponding to co-cited journal pairs in its refernces. For each article, positional statistics of z-scores were calculated to set thresholds for a binary (high/low) classification of conventionality (C) using the median and novelty (N) using the tenth percentile of z-scores within an article. Thus, HCLN would denote high conventionality and low novelty with all four combinations being possible. 
\cite{uzzi_atypical_2013} observed that HCHN articles were twice as likely to be highly cited, suggesting that novel combinations of ideas flavoring a body of conventional thought were a 'nearly universal` recipe for impact.
